Global Deaths Due to Air Pollution

### 2022-05-03 outline.Rmd
serbia year changed

* Which country has the highest average death count?
  + High Population: Pakistan
  + Low Population: Malawi
* Has the percentage of the affected population decreased or increased over time?
  + Generally it is decreasing for both High and Low populated countries 
* Which pollutant type has the greatest number of deaths?
  + High Population: Indoor Pollution
  + Low Population: Indoor Pollution
* How has the death count changed over the past two decades?
  + 1996-2006: 
    - High Population: Decreases
    - Low Population: Decreases
  + 2007-2017: 
    - High Population: Decreases 
    - Low Population: Decreases
* Which year and country had the highest number of deaths per pollutant type?
  + We looked at years 1996-2017 
  + Indoor: Pakistan and Malawi were mainly affected in 1996
  + Outdoor: Serbia and Pakistan were the top countries. 
    - 2011 was the worst for Pakistan. 
    - 2005 was the worst for Serbia 
    - Sri Lanka and Tonga increased, but Sri Lanka had a steep decrease after 2015 
  + Outdoor Ozone: Pakistan and Malawi were the top countries. 
    - 1997 was the worst for Pakistan. 
    - 1998 was the worst for Malawi
    - United States was the second highest amount of deaths among the higher populated countries
    - Pakistan decreased and then slightly increased
* Which is worse - outdoor or indoor pollution?
  + Inconclusive

>>>>

* Which country has the highest average death count?
  + High Population: Pakistan
  + Low Population: Malawi
* Has the percentage of the affected population decreased or increased over time?
  + Generally it is decreasing for both High and Low populated countries 
* Which pollutant type has the greatest number of deaths?
  + High Population: Indoor Pollution
  + Low Population: Indoor Pollution
* How has the death count changed over the past two decades?
  + 1996-2006: 
    - High Population: Decreases
    - Low Population: Decreases
  + 2007-2017: 
    - High Population: Decreases 
    - Low Population: Decreases
* Which year and country had the highest number of deaths per pollutant type?
  + We looked at years 1996-2017 
  + Indoor: Pakistan and Malawi were mainly affected in 1996
  + Outdoor: Serbia and Pakistan were the top countries. 
    - 2011 was the worst for Pakistan. 
    - 1997 was the worst for Serbia 
    - Sri Lanka and Tonga increased, but Sri Lanka had a steep decrease after 2015 
  + Outdoor Ozone: Pakistan and Malawi were the top countries. 
    - 1997 was the worst for Pakistan. 
    - 1998 was the worst for Malawi
    - United States was the second highest amount of deaths among the higher populated countries
    - Pakistan decreased and then slightly increased
* Which is worse - outdoor or indoor pollution?
  + Inconclusive
